Deeply Virtual Compton Scattering measurement off bound protons

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex
more implementation of clas comments

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations can be revealed through deeply virtual Compton scattering (DVCS), 
i.e., the hard exclusive lepto-production of a real photon, which provides 
access to a three-dimensional (3-D) imaging of partons within the generalized 
parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The measurement of free proton DVCS has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Defurne:2015kxq,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical step towards 
providing a similar 3-D picture of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case, however, two channels are 
available, the coherent channel where the scattering is off the entire nucleus, 
which is left intact in the final state \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS occurs on a 
nucleon, which is ejected from the nucleus. The latter is the focus of this 
letter and provides a unique access to the modification of the partonic 
structure of the bound nucleons \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}.  
The $^{4}$He nucleus is an ideal experimental target for this measurement as it 
is characterized by a strong binding energy, a relatively high nuclear core 
density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure can be performed, making this 
nucleus the perfect target for our investigation of the medium modifications of 
the nucleon's partonic structure.

@@

%background
The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. Our final asymmetries have been corrected for this 
contamination in the form of
$A_{LU~\text{corrected}}~=~\frac{1}{1~-~\text{contamination~percentage}}~A_{LU~\text{measured}}$. 
The $\pi^0$ contamination was estimated using detector simulation and 
experimental data. From simulation, we calculated the ratio ($R = 
N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  Then in 
each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
experimental DVCS events were calculated as $N = N^{ep\rightarrow 
e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events.  Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

%asymmetries
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

@@

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray band 
   represents the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations can be revealed through deeply virtual Compton scattering (DVCS), 
i.e., the hard exclusive lepto-production of a real photon, which provides 
access to a three-dimensional (3-D) imaging of partons within the generalized 
parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The measurement of free proton DVCS has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Defurne:2015kxq,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical step towards 
providing a similar 3-D picture of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case, however, two channels are 
available, the coherent channel where the scattering is off the entire nucleus, 
which is left intact in the final state \cite{Hattawy:2017woc}, and the 
incoherent channel where the DVCS occurs on a nucleon, which is ejected from 
the nucleus. The latter is the focus of this letter and provides a unique 
access to the modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}.  The $^{4}$He nucleus is an ideal 
experimental target for this measurement as it is characterized by a strong 
binding energy, a relatively high nuclear core density, and a large EMC 
effect~\cite{JSeely}. Moreover, it remains simple enough that precise 
calculation of its structure can be performed, making this nucleus the perfect 
target for our investigation of the medium modifications of the nucleon's 
partonic structure. The previous measurements of DVCS off nuclei, and in 
particular off $^4$He, performed at HERMES \cite{Airapetian:2009cga} yielded 
results with both "coherent enriched" and "incoherent enriched" event samples, 
hence not fully exclusive, but significant enough to be compared with our 
results below.

@@

%background
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. Our final asymmetries have been corrected for this 
contamination in the form of
$A_{LU~\text{corrected}}~=~\frac{1}{1~-~\text{contamination~percentage}}~A_{LU~\text{measured}}$. 
The $\pi^0$ contamination was estimated using detector simulation and 
experimental data. From simulation, we calculated the ratio ($R = 
N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  Then in 
each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
experimental DVCS events were calculated as $N = N^{ep\rightarrow 
e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events.  Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

%asymmetries

@@

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=7.8cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray band 
   represents the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
